---
title: "fars_function"
author: "Min Park"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fars_function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette briefly show the steps from loading Fatality Analysis Reporting System (FARS) data to several analyses including geographical plots

```{r}
library(fars)
```

## Read data

The function `fars_read_years` reads data of specific year and return tibbles for vectors of that year. This function uses related helper functions including fars_read and make_filename.

```{r read_data}
fars_read_years(2013)
```

## Summarize monthly fatalities

The function `fars_summarize_years` shows fatalities for given year summarized by month.

```{r summarize_data}
fars_summarize_years(2013)
```

## Plot on the map

The function `fars_map_state` plots the fatalities for a given year on the map of the state matching the state id.

```{r plot_data}
fars_map_state(1,2013)
```
